\begin{thebibliography}{9}
    \makeatletter
    \renewcommand\@biblabel[1]{{#1.}}
    \makeatother
    \bibitem{Soler2017}
    Soler J., Wanner L. On the relevance of syntactic and discourse features for author profiling and identification. Proceedings of the 15th Conference of the European Chapter of the Association for Computational Linguistics: Vol. 2. Short Papers. 2017. P. 681–687.
    
    \bibitem{Gomez-Adorno2018}
    Gómez-Adorno H., Posadas-Durán J.P., Sidorov G. Document embeddings learned on various types of n-grams for cross-topic authorship attribution. Computing. 2018. P. 1–16.
    
    \bibitem{Baturin2022}
    Батурин М.М., Белов Ю.С. Использование сверточных, рекуррентно-сверточных нейронных сетей и метода опорных векторов для определения авторства текста // Научные исследования в современном мире. Теория и практика: сборник избранных статей Всероссийской (национальной) научно-практической конференции. СПб., 2022. С. 47–49.
    
    \bibitem{Zhang2018}
    Zhang R., Hu Z., Guo H. Syntax encoding with application in authorship attribution. Proceedings of the 2018 Conference on Empirical Methods in Natural Language Processing. 2018. P. 2742–2753.
    
    \bibitem{Sundararajan2018}
    Sundararajan K., Woodard D. What represents ‘style’ authorship attribution? Proceedings of the 27th International Conference on Computational Linguistics. 2018. P. 2814–2822.
    
    \bibitem{Baturin2022}
    Батурин М.М., Белов Ю.С. Использование сверточных нейронных сетей, долгой краткосрочной памяти и оценок внимания для различения авторства текста // E-Scio [Электронный ресурс]. URL: http://e-scio.ru/wp-content/uploads/2022/01/Батурин-М.-М.-Белов-Ю.-С.pdf (дата обращения: 23.05.2022).
    
    \bibitem{Shen2017}
    Shen T., Lei T., Barzilay R. Style transfer from nonparallel text by cross-alignment. Proceedings of Advances in Neural Information Processing Systems 30. 2017. P. 6833–6844.
    
    \bibitem{Shrestha2017}
    Shrestha P., Sierra S., González F. Convolutional Neural Networks for Authorship Attribution of Short Texts. Proceedings of the 15th Conference of the European Chapter of the Association for Computational Linguistics: Vol. 2. Short Papers. 2017. P. 669–674.
    
    \bibitem{Stamatatos2017}
    Stamatatos E. Authorship Attribution Using Text Distortion. Proceedings of the 15th Conference of the European Chapter of the Association for Computational Linguistics: Vol. 1. Long Papers. 2017. P. 1138–1149.
    
    \end{thebibliography}